Automating Political Bias Prediction

### 2016-03-30 manuscript/political_bias_prediction.tex
More results in tables

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrrrrrr}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
      Linke     &  0.61    &  0.61  &    0.61   &   2315 &  0.81   &   0.76   &   0.79     &  104\\
     Gr\"une   &    0.65    &  0.64   &   0.64 &     3050 & 0.57  &     0.21  &    0.31    &   110\\
        SPD     &  0.55    &  0.55  &   0.55 &    2608 & 0.10  &    0.50   &   0.16    &    16\\
        CDU/CSU    &   0.68    &  0.70  &    0.69  &    3837 & 0.06   &   0.08  &    0.07   &     38 \\
\hline
avg / total    &   0.63  &    0.63  &    0.63 &    11810 & 0.57   &   0.42    &  0.45  &     268\\
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_four_classes}
Classification performance on the four party prediction problem; while classification on held-out data from parliament speeches was on average higher than on party programs, also on the completely out-of-training-sample data the model obtained reasonable accuracies in some cases. 
}
\end{table}

@@

>>>>

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrrrrrr}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
       cducsu   &    0.62  &    0.81  &    0.70  &     706&0.26    &  0.58   &   0.36    &  2030\\
        fdp    &   0.70   &   0.37  &    0.49    &   331&0.38   &   0.28    &  0.33   &   2319\\
     gruene &      0.59  &    0.40   &   0.48   &    298&0.47  &    0.20   &   0.28 &     3747\\
      linke    &   0.71   &   0.61  &    0.65    &   338&0.30   &   0.47   &   0.37    &  1701\\
        spd   &    0.60   &   0.69  &    0.65   &    606&0.26   &   0.16   &   0.20  &    2278\\
\hline
avg / total &      0.64   &   0.63   &   0.62    &  2279 &0.35    &  0.31 &     0.30   &  12075
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_four_classes}
Classification performance on the party affiliation prediction problem for data from the 17th legislative period on test set and evaluation set, respectively. Chance level is at 0.2.  
}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrrrrrr}
& \multicolumn{4}{c}{\bf Held-out parliament speeches} & \multicolumn{4}{c}{\bf Party Manifestos}\\
    &         precision    &recall &  f1-score  & N    &         precision    &recall &  f1-score  & N\\
\hline \hline
government    &   0.83   &   0.84&      0.84     & 1037 & 0.49  &    0.59 &     0.54  &    4349\\
 opposition     &  0.86  &    0.86   &   0.86    &  1242 & 0.74 &     0.66  &    0.70   &   7726\\
\hline
avg / total   &    0.85 &     0.85 &     0.85  &    2279 & 0.65  &     0.63  &     0.64  &    12075\\

%
\end{tabular}
\end{center}
\caption{
\label{tab:results_binary}
Classification performance on the binary prediction problem in the 17th legislative period, categorizing speeches to government (FDP/CDU/CSU) and opposition (Linke, Gr\"une, SPD).
}
\end{table}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{lrrrr}
    &         precision    &recall &  f1-score  & N\\
\hline\hline
test set    &  0.48   &   0.47  &    0.47  &    2651\\
evaluation set    &  0.47    &  0.46 &     0.46 &     2946\\
%
\end{tabular}
\end{center}
\caption{
\label{tab:results_avg_political_view}
Classification performance on the 56 class prediction problem of political views, see \autoref{sec:data}; chance performance would be around 0.02.
}
\end{table}
